A formalization of semi-simplicial and semi-cubical sets in dependent type theory

### 2023-01-10 paper/paper.tex
paper: more polish

\subsection{Homotopy type theory}
Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}. HoTT is based on the notion of a basic Type, and the notion of sets can be recovered as \U, where $\U$ is a straightforward packaging of two fields:

@@

\subsection{Fibered versus indexed representation}
It is well-known in set theory, that families of small sets can be represented in a fibered or indexed way. In the fibered way, a family over $T$ is represented a pair of a set $S$, and a function $S \rightarrow T$. The function classifies the original set into fibers. In contrast, in the indexed way, a family over $T$ is represented as a functional relation with domain $T$, which itself, by replacement axiom, is a set.

@@

\begin{align*}
  X_0 & : \U                                                                        \\
  X_1 & : X_0 \times X_0 \rightarrow \U                                             \\
  X_2 & : \forall a b c d, X_1 (a, b) \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
      & \rightarrow X_1 (c, d) \rightarrow \U                                       \\
  \ldots
\end{align*}

@@

\begin{align*}
  \framep[n][p](D) & \defeq & \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .        \\
                   &        & \layer[n][0](D)) \ldots) .\; \layer[n][p](D)                 \\
  \filler[n][p](D) & \defeq & \Sigma l_p : \layer[n][p](D) .                               \\
                   &        & (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
\end{align*}

@@

\subsection{Formal construction in ITT\label{sec:itt}}
\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}

>>>>

\subsection{Homotopy type theory}
Homotopy type theory (HoTT) is a logical foundation based on Martin-Löf type theory and the univalence axiom~\cite{hottbook}. HoTT is based on the notion of a basic \Type, and the notion of sets can be recovered as \U, where $\U$ is a straightforward packaging of two fields:

@@

\subsection{Fibered versus indexed representation}
It is well-known in set theory that families of small sets can be represented in a fibered or indexed way. In the fibered way, a family over $T$ is represented a pair of a set $S$, and a function $S \rightarrow T$. The function classifies the original set into fibers. In contrast, in the indexed way, a family over $T$ is represented as a functional relation with domain $T$, which itself, by replacement axiom, is a set.

@@

\begin{align*}
  X_0 & :                             & \U                                            \\
  X_1 & :                             & X_0 \times X_0 \rightarrow \U                 \\
  X_2 & : \forall a b c d, X_1 (a, b) & \rightarrow X_1 (a, c) \rightarrow X_1 (b, d) \\
      &                               & \rightarrow X_1 (c, d) \rightarrow \U         \\
  \ldots
\end{align*}

@@

\begin{align*}
  \framep[n][p](D) & \defeq & \Sigma a_n : (\ldots (\Sigma \unitpoint : \unittype .\; \layer[n][0](D)) \ldots) . \\
                   &        & \layer[n][p](D)                                                                    \\
  \filler[n][p](D) & \defeq & \Sigma l_p : \layer[n][p](D) .                                                     \\
                   &        & (\ldots (\Sigma l_n : \layer[n][n - 1](D) .\; D.\tl) \ldots)
\end{align*}

@@

\subsection{Formal construction in ITT\label{sec:itt}}
\renewcommandx{\cohf}{\coh{frame}[][][][][][][][]}
\renewcommandx{\cohl}{\coh{layer}[][][][][][][][]}
